The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-01-25 analysis/paper/paper.qmd
finalisezed and applied cleaning functions'

```{r}
#| label: setup

# Load packages ----
library(here)
library(dplyr)
library(readr)
library(stringr)
library(tidytext)
library(pluralize)
library(tm)
devtools::load_all(".")

# Read thesis metadata ----
emu_theses <- read_csv(here::here("analysis","data", "raw_data", "theses-metadata.csv")) %>%
  mutate(text = "")

pdf_names <- dir(here::here("analysis", "data", "raw_data"), pattern = "*.pdf")

emu_theses <- emu_theses %>%
  filter(file_name %in% pdf_names)

pdf_paths <- here::here("analysis","data", "raw_data", emu_theses$file_name)

@@

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  str_replace_all("\\s", " ") %>%  ### remove all carriage return and newline characters
  str_replace_all("- ", "") %>%       ### remove all hyphens
  str_replace_all("[0-9]", "") %>%    ### remove all numbers
  str_replace_all(emu_theses$first_name, "") %>%   ### remove author first name
  str_replace_all(emu_theses$last_name, "") %>%     ### remove author surname
  str_replace_all(emu_theses$title, "") %>%              ### remove title
  str_replace_all("EMU", "") %>%           ### remove common words
  str_squish()
```

@@

Stop words:
- Custom stop words from titles and author names should only be removed from corresponding theses;
- Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as custom stop words;
- All theses were written in English; for common English stop words the "snowball" lexicon was used.

```{r}
stop_words_custom <- emu_theses %>% 
  unnest_tokens(output = word, input = title) %>%   ### add words from the title
  select(word) %>% 
  rbind(., data.frame(word = c("preface", "foreword", "introduction", "conclusion", "thesis"))) %>% 
  rbind(., data.frame(word = c("city", "urban", "urbanism"))) %>% 
  rbind(., data.frame(word = c("hab", "km")))

emu_theses_words <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(output = word, input = text) %>%   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") %>%  # remove stop words
  anti_join(stop_words_custom, by = "word")
```

```{r}
# find the most frequently used words
emu_theses_top <- emu_theses_words %>%
  group_by(title) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  filter(n > 50) %>%              ### filter words with a minimum count
  ungroup() %>% 
  mutate(word = reorder(word, n))

emu_theses_top[emu_theses_top$word == "ring",]

emu_theses_top %>%
  ggplot(aes(x = word, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2)

# # wip function ngrams
# get_ngrams <- function(df, n) {
#   if (!is.numeric(n)) {
#     stop("n is not numeric")
#   }
#   emu_theses %>%
#     mutate(author = paste(first_name, last_name)) %>% 
#     select(author, title, text, -c(year, first_name, last_name, text_start, text_end)) %>% 
#     unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
#     separate(bigram, into = c("first","second"), sep = " ", remove = FALSE) %>%
#     anti_join(stop_words, by = c("first" = "word")) %>%
#     anti_join(stop_words, by = c("second" = "word")) %>%
#     anti_join(stop_words_custom, by = c("first" = "word")) %>%
#     anti_join(stop_words_custom, by = c("second" = "word")) %>%
#     filter(str_detect(first, "[a-z]") & str_detect(second, "[a-z]")) %>% 
#     filter(first != second) %>% 
#     filter(first != "source")
# }
# emu_theses_ngrams <- get_ngrams(emu_theses, 2)

# bigrams
emu_theses_bigrams <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
  separate(bigram, into = c("first","second"), sep = " ", remove = FALSE) %>%
  anti_join(stop_words, by = c("first" = "word")) %>%
  anti_join(stop_words, by = c("second" = "word")) %>%
  anti_join(stop_words_custom, by = c("first" = "word")) %>%
  anti_join(stop_words_custom, by = c("second" = "word")) %>%
  filter(str_detect(first, "[a-z]") & str_detect(second, "[a-z]")) %>% 
  filter(first != second) %>% 
  filter(first != "source")

emu_theses_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 10) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() %>% 
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top %>%
  ggplot(aes(x = bigram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2)

# find the most frequently used bigrams
emu_thesis_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>% 
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 10) %>%                   ### change the number of top words to show
  mutate(bigram = reorder(bigram, n)) %>% 
  print()
```

>>>>

```{r}
#| label: setup
library(dplyr)
library(readr)
library(stringr)
devtools::load_all(".")

# read csv file with pages that are useful for the analysis
emu_theses <- read_csv(here::here("analysis","data", "raw_data", "emu-theses.csv")) %>%
  mutate(pdf_filename = paste0(year, "-", author_surname, ".pdf")) %>%
  mutate(text = "")

pdf_names <- dir(here::here("analysis","data", "raw_data"), pattern = "*.pdf")

emu_theses <- emu_theses %>%
  filter(pdf_filename %in% pdf_names)

pdf_paths<- here::here("analysis","data", "raw_data", emu_theses$pdf_filename)

@@

#head_text(emu_theses$text)

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )

```

@@
